What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-29 paper/main.tex
fixed passive voice

%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
%\paragraph{Real-world datasets}
{\bf Feasibility.}
We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
%
We gather a test suite totalling 91 formulas from two real-world requirement specification applications. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas from the suite of $23$ collections of formulas were collected. We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.

We run \texttt{ltl2regex} on these $91$ examples: $87$ of the $91$ input formulas complete execution within a timeout of $20$ seconds for the feasibility tests. Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of. We are able to generate tractable visualization on the remaining $85$, or over $93\%$ of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

>>>>

%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
%\paragraph{Real-world datasets}
{\bf Feasibility.}
We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
%
We gather a test suite totalling 91 formulas from two real-world requirement specification applications. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas extracted from the suite of $23$ collections of formulas. We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.

We run \texttt{ltl2regex} on these $91$ examples: $87$ of the $91$ input formulas complete execution within a timeout of $20$ seconds for the feasibility tests. Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of. We are able to generate tractable visualization on the remaining $85$, or over $93\%$ of benchmarks tested. The plots of visualization complexity on these formula appear below in \cref{fig:real-world}.
